Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-09-17 paper/paper.tex
Update paper

There are many different molecule groups that are being looked at for use as organic solar cells \hl{[CITE]}. One such group is the benzobisazoles \hl{[CITE]}. To optimize the optoelectronic properties of molecules for use in solar cells, various electron donating and electron accepting groups are added to the structure to shift electron density. For testing all of the possible structures (even in small sets) this is not feasible in the lab. To reduce some of the time required, and to expand the total search space, computational methods such as density functional theory have been used to predict the properties of molecules fairly rapidly. Unfortunately, these calculations also have their own limits in the amount of structures that can be tested in a reasonable time frame.
 \hl{There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE]. To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.}

@@

\begin{equation}\label{decay2}
    V = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
\end{equation}

@@

\subsection{Coulomb Matrix}
(Montavon et al.)
$$
M_{ij} =
\begin{cases}
    0.5 Z_i^{2.4} &: i = j \\
    \frac{Z_i Z_j}{|R_i - R_j|} &: i \ne j \\
\end{cases}
$$
Specifically, to reduce the dimensionality Principal Component Analysis was used to reduce these vectors from 52,000 elements to 500 elements.

@@

In the results there is a large increase in the performance of the linear models (linear regression and linear ridge regression) when using the decay vector with predictions. This can be largely accounted for the linear relation between the HOMO, the LUMO, and the Band Gap energy levels $$BandGap \approx 0.93 (LUMO - HOMO) - 0.15$$.

@@

\hl{Also, the methods mentioned in }\cite{hansen_assessment_2013} \hl{were tested and the results were not as good as any of the other name based features (0.25-0.35 eV). In addition to the accuracy problems, it had severe performance problems because it relies on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure. To save time, only structures with $<45$ atoms total were tested, leaving about 450 structures. Attempting the full data set is not feasible with all the structures/atoms. By using all the structures and using PCA to reduce the dimensionality down from 52,000 to 500 retains 99.97\% of the variability of the data (0.24 $\pm$ 0.04 eV MAE). To run the full data set it is expected to take on the order of 10s to 100s of days. (plus SVM does not work well when features >> samples)}

@@

\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), XSEDE (Blacklight, Gordon, Trestles), University of North Georgia Department of Chemistry and Biochemistry, ...}

@@

OTHER
numpy, scipy, matplotlib

@@

All of the actual machine learning code:

>>>>

In recent years there has been a large interest in the creation of organic solar cells instead in lieu of their inorganic counterparts. The main driving reasons for such advancements are because organic solar cells are cheaper to manufacture, and they are also are \"cleaner\".
\hl{Organic solar cells have been a hot topic in chemistry and material science research... much of the work involving permuting many different structures } \hl{150,000, 156,314 cores, 1.21 petaflops Mark Thompson USC}
There are many different molecule groups that are being looked at for use as organic solar cells \hl{[CITE]}. The structures often are composed of many similar features such as polymeric structures and highly conjugated systems. One possible group of structures are the benzobisazoles \hl{[CITE]}. In previous work, various benzobisazoles have been shown to have interesting optoelectronic properties, thus making them viable for use as organic solar cells\hl{[CITE]}.

To optimize the optoelectronic properties of molecules for use in solar cells, various electron donating and electron accepting groups are added to the structure to shift electron density. For testing all of the possible structures (even in small sets) this is not feasible in the lab. To reduce some of the time required, and to expand the total search space, computational methods such as density functional theory have been used to predict the properties of molecules fairly rapidly. Unfortunately, these calculations also have their own limits in the amount of structures that can be tested in a reasonable time frame.
 \hl{There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE]. To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.}

@@

\begin{equation}\label{decay2}
    V = \sum_i^n \left[A \left(\frac{d_i}{M_i}\right)^{-H} \right]^{p}
\end{equation}

@@

\subsection{Coulomb Matrix}
For the work by Montavon et al, they make use of a feature structure that depends on the atomic number, and the coordinates of each atom in the structure. From that, they construct a distance matrix of the following form of which they call the Coulomb Matrix.

$$
M_{ij} =
\begin{cases}
    0.5 Z_i^{2.4} & i = j \\
    \frac{Z_i Z_j}{|R_i - R_j|} & i \ne j \\
\end{cases}
$$
Specifically, to reduce the dimensionality Principal Component Analysis was used to reduce these vectors from 52,000 elements to 500 elements.

@@

In the results there is a large increase in the performance of the linear models (linear regression and linear ridge regression) when using the decay vector with predictions. This can be largely accounted for the linear relation between the HOMO, the LUMO, and the Band Gap energy levels.

$$BandGap \approx 0.93 (LUMO - HOMO) - 0.15$$

@@

\hl{Also, the methods mentioned in }\cite{hansen_assessment_2013} \hl{were tested and the results were not as good as any of the other name based features (0.25-0.35 eV). In addition to the accuracy problems, it had severe performance problems because it relies on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure. To save time, only structures with $<45$ atoms total were tested, leaving about 450 structures. Attempting the full data set is not feasible with all the structures/atoms. By using all the structures and using PCA to reduce the dimensionality down from 52,000 to 500 retains 99.97\% of the variability of the data (0.24 $\pm$ 0.04 eV MAE). To run the full data set it is expected to take on the order of 10s to 100s of days. (plus SVM does not work well when $N_{features} >> N_{samples}$)}

@@

\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), XSEDE (Blacklight, Gordon, Trestles), University of North Georgia Department of Chemistry and Biochemistry, Carnegie Mellon Department of Chemistry, ...}

@@

numpy, scipy, matplotlib

@@

All of the machine learning code:
